Using the sim package with different input classes

### 2022-06-13 data-raw/si-classes.Rmd
Update name in library calls #20
Update all URLs #20
Update urls
Rename pkg with changer, close #20
Former-commit-id: 6c6fe93a3cbf6dac23e5eae172f3e6a4e4332fba

---
title: "Using the si package with different input classes"
output: github_document
---

@@

```{r setup}
# remotes::install_github("robinlovelace/si")
library(si)
# ?si_predict
```

>>>>

---
title: "Using the sim package with different input classes"
output: github_document
---

@@

```{r setup}
# remotes::install_github("robinlovelace/sim")
library(sim)
# ?si_predict
```
